### 2022-06-24 input/related_work.tex
quick format

\noindent A central server that registers both these information
facilitates the computation, for it gathers all knowledge in one
place~\cite{snamp, p2p-oracle, fogstore, p2p-alto}. However, it comes with
well-known issues such as load balancing, or single point of failure.
%% Numerous solutions
%% maintain an index of all replica locations on a centralized
%% server. This comes with well-known disadvantages inherent to
%% centralized solutions such as load balancing, robustness or locality
%% that are even magnified in an Edge context.

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
  coin_19}, but still raises locality issues where \processes
\begin{inparaenum}[(i)]
\item request to possibly far away location services the content
  location, and then
\item request the actual content from possibly far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
Hash values are keys to retrieve the associated content location.
Before downloading any content, a \node requests its location using
its key. After round-trips between possibly distant DHT servers, the
\node gets available replicas. Contrarily to \NAME, such services do
not ensure to include the closest replica.

@@

\noindent In addition, they often do not include distance information
along with replica location. Determining where resides the closest
replica for every requesting \process necessarily involves some
knowledge about the \emph{current} topology.  Maintaining a consistent
view of an ever changing topology across a network is inherently
complicated~\cite{topology-discovery, ospf}.
%%  As for the index, this knowledge about the topology can be either
%% centralized~\cite{topology-discovery} or distributed like in
%% routing protocols such as \underline{O}pen \underline{S}hortest
%% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
As a consequence, the requesting \node ends up downloading from multiple
replica hosts, yet only keeping the fastest answer. \Processes either
waste network resources, or face lower response time.

>>>>

\noindent A central server that registers both these information
facilitates the computation, for it gathers all knowledge in one
place~\cite{snamp,p2p-oracle,fogstore,p2p-alto}. However, it comes with
well-known issues such as load balancing, or single point of failure.
%% Numerous solutions
%% maintain an index of all replica locations on a centralized
%% server. This comes with well-known disadvantages inherent to
%% centralized solutions such as load balancing, robustness or locality
%% that are even magnified in an Edge context.

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet,ipfs,mdht,squirrel,triukose2011measuring,coin_19}, but still raises locality issues where \processes
\begin{inparaenum}[(i)]
\item request to possibly far away location services the content
  location, and then
\item request the actual content from possibly far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs,mdht,squirrel}, each \process
stores a part of the index defined by an interval between hash values.
Hash values are keys to retrieve the associated content location.
Before downloading any content, a \node requests its location using
its key. After round-trips between possibly distant DHT servers, the
\node gets available replicas. Contrarily to \NAME, such services do
not ensure to include the closest replica.

@@

\noindent In addition, they often do not include distance information
along with replica location. Determining where resides the closest
replica for every requesting \process necessarily involves some
knowledge about the \emph{current} topology.  Maintaining a consistent
view of an ever changing topology across a network is inherently
complicated~\cite{topology-discovery,ospf}.
%%  As for the index, this knowledge about the topology can be either
%% centralized~\cite{topology-discovery} or distributed like in
%% routing protocols such as \underline{O}pen \underline{S}hortest
%% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
As a consequence, the requesting \node ends up downloading from multiple
replica hosts, yet only keeping the fastest answer. \Processes either
waste network resources, or face lower response time.

### 2022-06-24 input/tablerelatedwork.tex
quick format

  \NO{Centralized}~\cite{snamp, p2p-oracle, fogstore, p2p-alto} & \rxmark & one & \cmark & R\\
  DHT~\cite{ipfs, mdht, squirrel}                               & \rxmark & few & \cmark & R\\

@@

  Vector-based routing~\cite{nlsr, ospf}   & \cmark & \NO{all} & \cmark & R/C\\
  Replicated store~\cite{shapiro2011crdts} & \cmark & \NO{all} & \cmark & R/C\\

@@

  Timeout-based~\cite{garcia-lopez, hemmati2015namebased}   & \cmark & scope & \rxmark & \NO{C}\\
  Random walks~\cite{sohier2012physarum} & \cmark & scope & \cmark  & \NO{C}\\
  Spanning Forest~\cite{barjon2014maintaining} & \cmark & scope & \cmark & \NO{C}\\

>>>>

  \NO{Centralized}~\cite{snamp,p2p-oracle,fogstore,p2p-alto} & \rxmark & one & \cmark & R\\
  DHT~\cite{ipfs,mdht,squirrel}                               & \rxmark & few & \cmark & R\\

@@

  Vector-based routing~\cite{nlsr,ospf}   & \cmark & \NO{all} & \cmark & R/C\\
  Replicated store~\cite{shapiro2011crdts} & \cmark & \NO{all} & \cmark & R/C\\

@@

  Timeout-based~\cite{garcia-lopez,hemmati2015namebased}   & \cmark & scope & \rxmark & \NO{C}\\
  Random walks~\cite{sohier2012physarum} & \cmark & scope & \cmark  & \NO{C}\\
  Spanning Forest~\cite{barjon2014maintaining} & \cmark & scope & \cmark & \NO{C}\\
